---
title: "India Air Quality Index Forecast: ARMA_GARCH"
author: "Welly (Wei-Chung) Huang"
date: "2024-05-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 6)
setwd("~/Documents/University of Chicago/ADSP 31006 Time Series Analysis & Forecasting/Project/india-air-quality-index-forecast/scripts/modeling")
options(width = 200)
```

# Import Packages

```{r, message=FALSE, warning=FALSE}
Sys.setlocale("LC_TIME", "English")
library(readr)
library(xts)
library(forecast)
library(tseries)
library(fGarch)
library(TSA)
library(Metrics)
library(lmtest)
library(gridExtra)
library(ggplot2)
library(cowplot)
library(gridGraphics)
library(grid)
```

# Import Datasets

```{r}
cities <- c('bengaluru', 'lucknow', 'delhi', 'chennai')
path <- '/Users/kshitizsahay/Documents/University of Chicago/ADSP 31006 Time Series Analysis & Forecasting/Project/india-air-quality-index-forecast/data/preprocessed_dataset/daily/'

for (city in cities) {
  file_name <- paste0(path, city, "_day_filled.csv")
  assign(city, read.csv(file_name))
  print(rbind(head(get(city), 3), tail(get(city), 3)))
}
```

# Create XTS objects

```{r}
for (city in cities) {
  data <- get(city)
  data$Date <- as.Date(data$Date)
  city_xts <- xts(data[,-1], order.by = data$Date)
  assign(paste0(city, "_xts"), city_xts)
  print(city)
  print(rbind(head(get(paste0(city, "_xts")), 3), tail(get(paste0(city, "_xts")), 3)))
}
```

# EDA

```{r}
cities <- c('bengaluru', 'lucknow', 'delhi', 'chennai')
cities_xts <- c('bengaluru_xts', 'lucknow_xts', 'delhi_xts', 'chennai_xts')

plot(bengaluru_xts$AQI)
plot(lucknow_xts$AQI)
plot(delhi_xts$AQI)
plot(chennai_xts$AQI)
```

```{r}
eda_ts <- function (xts, city_name) {
  acf(xts$AQI, main = paste("ACF for", city_name))
  pacf(xts$AQI, main = paste("PACF for", city_name))
  acf((xts$AQI)^2, main = paste("ACF for", city_name, "squared"))
}

for (city in cities_xts) {
  eda_ts(get(city), city)
}
```

```{r}
adf.test(bengaluru_xts$AQI)
kpss.test(bengaluru_xts$AQI)
eacf(bengaluru_xts$AQI)

adf.test(chennai_xts$AQI)
kpss.test(chennai_xts$AQI)
eacf(chennai_xts$AQI)

adf.test(delhi_xts$AQI)
kpss.test(delhi_xts$AQI)
eacf(delhi_xts$AQI)

adf.test(lucknow_xts$AQI)
kpss.test(lucknow_xts$AQI)
eacf(lucknow_xts$AQI)
```

# Decompose

```{r}
for (city in cities_xts) {
  plot(decompose(ts(get(city)$AQI, frequency = 365)), col.main = "white")
  title(main = paste("Decomposition of additive time series for", city))
}
```

# Train / Test Split

```{r}
for (city in cities_xts) {
  train_data <- window(get(city),
                       start = as.Date("2015-01-01"),
                       end = as.Date("2020-06-01"))
  test_data <- window(get(city),
                      start = as.Date("2020-06-02"),
                      end = as.Date("2020-07-01"))
  assign(paste0(city, "_train"), train_data)
  assign(paste0(city, "_test"), test_data)
}

# ls(pattern = "_train")
# ls(pattern = "_test")
```

# Initial Model
ARMA and GARCH combination = arma(1,1) + garch(1,1)

```{r}
AG <- function (train, test) {
  train_data <- get(train)
  test_data <- get(test)

  normalized_ts <- (train_data$AQI - mean(train_data$AQI)) / sd(train_data$AQI)
  model <- garchFit(formula = ~ arma(1,1) + garch(1,1),
                    data = normalized_ts, trace = FALSE)
  summary <- summary(model)
  BIC <- summary[["ics"]][["BIC"]]
  
  stat_values <- summary$stat_tests # Standardized Residuals Tests
  Jarque_Bera_R_pv <- stat_values[10]
  Shapiro_Wilk_pv <- stat_values[11]
  Ljung_Box_R_Q10_pv <- stat_values[12]
  Ljung_Box_R_Q15_pv <- stat_values[13]
  Ljung_Box_R_Q20_pv <- stat_values[14]
  Ljung_Box_R2_Q10_pv <- stat_values[15]
  Ljung_Box_R2_Q15_pv <- stat_values[16]
  Ljung_Box_R2_Q20_pv <- stat_values[17]
  LM_Arch_pv <- stat_values[18]
  
  forecast <- predict(model, n.ahead = 30)
  value <- forecast$meanForecast * sd(train_data$AQI) + mean(train_data$AQI)
  rmse <- rmse(as.numeric(test_data$AQI), value)
  mae <- mae(as.numeric(test_data$AQI), value)
  mape <- mape(as.numeric(test_data$AQI), value)
  amape <- mean(100 * abs(as.numeric(test_data$AQI) - value)/as.numeric(test_data$AQI))

  return(list(model = model,
              summary = summary,
              BIC = round(BIC, 4),
              Jarque_Bera_R_pv = round(Jarque_Bera_R_pv, 4),
              Shapiro_Wilk_pv = round(Shapiro_Wilk_pv, 4),
              Ljung_Box_R_Q10_pv = round(Ljung_Box_R_Q10_pv, 4),
              Ljung_Box_R_Q15_pv = round(Ljung_Box_R_Q15_pv, 4),
              Ljung_Box_R_Q20_pv = round(Ljung_Box_R_Q20_pv, 4),
              Ljung_Box_R2_Q10_pv = round(Ljung_Box_R2_Q10_pv, 4),
              Ljung_Box_R2_Q15_pv = round(Ljung_Box_R2_Q15_pv, 4),
              Ljung_Box_R2_Q20_pv = round(Ljung_Box_R2_Q20_pv, 4),
              LM_Arch_pv = round(LM_Arch_pv, 4),
              forecast = value,
              RMSE = round(rmse, 4),
              MAE = round(mae, 4),
              MAPE = round(mape, 4),
              AMAPE = round(amape, 4)
              ))
}

plot_forecast_vs_real <- function(forecast, real_data, time_index, city) {
  forecast_df <- data.frame(Time = time_index, Value = as.numeric(forecast), Type = "Forecast")
  real_df <- data.frame(Time = time_index, Value = as.numeric(real_data), Type = "Real")
  plot_df <- rbind(forecast_df, real_df)
  
  p <- ggplot(plot_df, aes(x = Time, y = Value, color = Type)) +
    geom_line(size = 1) +
    ggtitle(paste("Forecast vs Real Data for", city)) +
    ylab("AQI") +
    xlab("Time") +
    theme_minimal() +
    scale_color_manual(values = c("Forecast" = "blue", "Real" = "red"))
  
  return(p)
}

df_AG <- data.frame(
  bengaluru_xts = numeric(14),
  lucknow_xts = numeric(14),
  delhi_xts = numeric(14),
  chennai_xts = numeric(14))

plot_list <- list()

for (city in cities_xts) {
  result <- AG(paste0(city, "_train"), paste0(city, "_test"))

  df_col <- c(
    result$Jarque_Bera_R_pv,
    result$Shapiro_Wilk_pv,
    result$Ljung_Box_R_Q10_pv,
    result$Ljung_Box_R_Q15_pv,
    result$Ljung_Box_R_Q20_pv,
    result$Ljung_Box_R2_Q10_pv,
    result$Ljung_Box_R2_Q15_pv,
    result$Ljung_Box_R2_Q20_pv,
    result$LM_Arch_pv,
    result$BIC,
    result$RMSE,
    result$MAE,
    result$MAPE,
    result$AMAPE)
  
  df_AG[city] <- df_col
  time_index <- index(get(paste0(city, "_test")))
  plot <- plot_forecast_vs_real(result$forecast, get(paste0(city, "_test"))$AQI,
                                time_index, city)
  plot_list[[city]] <- plot
}

rownames(df_AG) <- c("Jarque-Bera (R) pv",
                     "Shapiro-Wilk (R) pv",
                     "Ljung_Box (R, Q = 10) pv",
                     "Ljung_Box (R, Q = 15) pv",
                     "Ljung_Box (R, Q = 20) pv",
                     "Ljung_Box (R^2, Q = 10) pv",
                     "Ljung_Box (R^2, Q = 15) pv",
                     "Ljung_Box (R^2, Q = 20) pv",
                     "LM Arch pv",
                     "BIC",
                     "RMSE",
                     "MAE",
                     "MAPE",
                     "AMAPE")
df_AG
do.call(grid.arrange, c(plot_list, ncol = 2))
```

# Initial Conclusion
Normality Tests (Jarque-Bera and Shapiro-Wilk):
The standardized residuals are not normally distributed for any of the datasets.

Autocorrelation Tests (Ljung-Box for residuals):
There is significant autocorrelation in the standardized residuals, indicating that the model has not fully captured the time-series dynamics. (The ARMA part)

Autocorrelation Tests for Squared Residuals (Ljung-Box for R^2):
For most cities, there is no significant autocorrelation in the squared residuals, suggesting that the GARCH model is effectively capturing the volatility clustering.

LM Arch Test
The GARCH model adequately captures the autoregressive conditional heteroskedasticity in the data.

Therefore, we should focus on changing the ARMA part of the ARMA-GARCH model since it has be proven that the GARCH part is handling the variances well.


# Use auto.arima() to see which pdq order works better

```{r}
arima <- function (train, test) {
  train_data <- get(train)
  test_data <- get(test)
  
  model <- auto.arima(train_data$AQI, seasonal = FALSE)
  summary <- summary(model)
  AICC <- model$aicc
  BIC <- model$bic
  residual_check <- checkresiduals(model)
  
  forecast <- forecast(model, h = 30)$mean
  mse <- mse(as.numeric(test_data$AQI), forecast)
  mae <- mae(as.numeric(test_data$AQI), forecast)
  mape <- mape(as.numeric(test_data$AQI), forecast)
  amape <- mean(100 * abs(as.numeric(test_data$AQI) - forecast)/as.numeric(test_data$AQI))
  
  return(list(summary = summary,
              residual_check = residual_check,
              AICC = AICC,
              BIC = BIC,
              forecast = forecast,
              MSE = mse,
              MAE = mae,
              MAPE = mape,
              AMAPE = amape
              ))
}

df_ARIMA <- data.frame()

for (city in cities_xts) {
  result <- arima(paste0(city, "_train"), paste0(city, "_test"))
  df_row <- c(paste("(",
                    result$summary$arma[1], ",",
                    result$summary$arma[6], ",",
                    result$summary$arma[2], ")"),
              round(result$residual_check$p.value, 4),
              round(result$AICC, 4),
              round(result$BIC, 4),
              round(result$MSE, 4),
              round(result$MAE, 4),
              round(result$MAPE, 4),
              round(result$AMAPE, 4))
  df_ARIMA <- rbind(df_ARIMA, df_row)
}

rownames(df_ARIMA) <- cities_xts
colnames(df_ARIMA) <- c('order', 'Ljung-Box pv', 'AICC', 'BIC', 'MSE', 'MAE', 'MAPE', 'AMAPE')

df_ARIMA
```

auto.arima() suggests:
Bengaluru = (1,1,1)
Lucknow =   (4,1,2)
Delhi =     (3,1,3)
Chennai =   (1,1,1)

However, when using (4,1,2) for Lucknow, the *forecast <- predict(model, n.ahead = 30)* part will have issues going over n.ahead = 3.

So, let's use a grid search to make sure we find the best ARMA model.

```{r}
arima_grid_search <- function (data, name, maxp, maxd = 2, maxq) {
  grid_table <- data.frame(data = character(),
                           order = character(),
                           aicc = numeric(),
                           bic = numeric())
  
  for (p in 0:maxp) {
    for (d in 0:maxd) {
      for (q in 0:maxq) {
          arima_model <- Arima(data$AQI, order = c(p, d, q))
          order <- paste("(", p, ",", d, ",", q, ")", sep = "")
          AICC <- arima_model$aicc
          BIC <- arima_model$bic
          row_data <- list(data = name, order = order, aicc = AICC, bic = BIC)
          grid_table <- do.call(rbind, list(grid_table, row_data))
          }
        }
      }
  sorted_grid <- grid_table[order(grid_table$bic), ]
  return(head(sorted_grid, 5))
}


arima_grid_search(bengaluru_xts_train, "bengaluru_xts_train", maxp = 5, maxq = 5)
arima_grid_search(lucknow_xts_train, "lucknow_xts_train", maxp = 3, maxq = 5)
arima_grid_search(delhi_xts_train, "delhi_xts_train", maxp = 5, maxq = 5)
arima_grid_search(chennai_xts_train, "chennai_xts_train", maxp = 5, maxq = 5)
```
Our final ARMA components:
Bengaluru = (1,1,1)
Lucknow =   (0,1,4)
Delhi =     (1,1,2)
Chennai =   (1,1,1)

# Final Models

## Differentiating

Before running the ARMA-GARCH model with the new ARMA orders, differentiate the xts objects first.
```{r}
for (city in cities_xts) {
  city_train <- paste0(city, "_train")
  city_diff <- paste0(city, "_train_diff")
  diff_data <- diff(get(city_train), differences = 1)
  diff_data <- diff_data[-1, ]
  assign(city_diff, diff_data)
}
```

Check if they are stationary

```{r}
for (city in cities_xts) {
  eda_ts(get(paste0(city, "_train_diff")), paste0(city, "_train_diff"))
}
```

## Final Model

Bengaluru = 111
Lucknow = 014
Delhi = 112
Chennai = 111

```{r}
AG2 <- function (train, test) {
  train_data <- get(train)
  test_data <- get(test)

  normalized_ts <- (train_data$AQI - mean(train_data$AQI)) / sd(train_data$AQI)

  if (train == 'bengaluru_xts_train_diff') {
    p_arma <- 1
    q_arma <- 1
  } else if (train == 'lucknow_xts_train_diff') {
    p_arma <- 0
    q_arma <- 4
  } else if (train == 'delhi_xts_train_diff') {
    p_arma <- 1
    q_arma <- 2
  } else {
    p_arma <- 1
    q_arma <- 1
  }
  formula <- bquote(~ arma(.(p_arma), .(q_arma)) + garch(1, 1))
  model <- garchFit(formula = formula, data = normalized_ts, trace = FALSE)
  # order <- paste0("ARMA(", p_arma, ",", q_arma, ")")
  summary <- summary(model)
  BIC <- summary[["ics"]][["BIC"]]

  stat_values <- summary$stat_tests # Standardized Residuals Tests
  Jarque_Bera_R_pv <- stat_values[10]
  Shapiro_Wilk_pv <- stat_values[11]
  Ljung_Box_R_Q10_pv <- stat_values[12]
  Ljung_Box_R_Q15_pv <- stat_values[13]
  Ljung_Box_R_Q20_pv <- stat_values[14]
  Ljung_Box_R2_Q10_pv <- stat_values[15]
  Ljung_Box_R2_Q15_pv <- stat_values[16]
  Ljung_Box_R2_Q20_pv <- stat_values[17]
  LM_Arch_pv <- stat_values[18]

  forecast <- predict(model, n.ahead = 30)
  value <- forecast$meanForecast * sd(train_data$AQI) + mean(train_data$AQI)
  rmse <- rmse(as.numeric(test_data$AQI), value)
  mae <- mae(as.numeric(test_data$AQI), value)
  mape <- mape(as.numeric(test_data$AQI), value)
  amape <- mean(100 * abs(as.numeric(test_data$AQI) - value)/as.numeric(test_data$AQI))

  return(list(model = model,
              summary = summary,
              # order = order,
              BIC = round(BIC, 4),
              Jarque_Bera_R_pv = round(Jarque_Bera_R_pv, 4),
              Shapiro_Wilk_pv = round(Shapiro_Wilk_pv, 4),
              Ljung_Box_R_Q10_pv = round(Ljung_Box_R_Q10_pv, 4),
              Ljung_Box_R_Q15_pv = round(Ljung_Box_R_Q15_pv, 4),
              Ljung_Box_R_Q20_pv = round(Ljung_Box_R_Q20_pv, 4),
              Ljung_Box_R2_Q10_pv = round(Ljung_Box_R2_Q10_pv, 4),
              Ljung_Box_R2_Q15_pv = round(Ljung_Box_R2_Q15_pv, 4),
              Ljung_Box_R2_Q20_pv = round(Ljung_Box_R2_Q20_pv, 4),
              LM_Arch_pv = round(LM_Arch_pv, 4),
              forecast = value,
              RMSE = round(rmse, 4),
              MAE = round(mae, 4),
              MAPE = round(mape, 4),
              AMAPE = round(amape, 4)
              ))
}

df_AG_2 <- data.frame(
  bengaluru_xts = numeric(14),
  lucknow_xts = numeric(14),
  delhi_xts = numeric(14),
  chennai_xts = numeric(14))

for (city in cities_xts) {
  result <- AG2(paste0(city, "_train_diff"), paste0(city, "_test"))
  
  df_col <- c(
    result$Jarque_Bera_R_pv,
    result$Shapiro_Wilk_pv,
    result$Ljung_Box_R_Q10_pv,
    result$Ljung_Box_R_Q15_pv,
    result$Ljung_Box_R_Q20_pv,
    result$Ljung_Box_R2_Q10_pv,
    result$Ljung_Box_R2_Q15_pv,
    result$Ljung_Box_R2_Q20_pv,
    result$LM_Arch_pv,
    result$BIC,
    result$RMSE,
    result$MAE,
    result$MAPE,
    result$AMAPE)
  
  df_AG_2[city] <- df_col
  time_index <- index(get(paste0(city, "_test")))
  plot <- plot_forecast_vs_real(result$forecast, get(paste0(city, "_test"))$AQI,
                                time_index, city)
  plot_list[[city]] <- plot
}

rownames(df_AG_2) <- c("Jarque-Bera (R) pv",
                       "Shapiro-Wilk (R) pv",
                       "Ljung_Box (R, Q = 10) pv",
                       "Ljung_Box (R, Q = 15) pv",
                       "Ljung_Box (R, Q = 20) pv",
                       "Ljung_Box (R^2, Q = 10) pv",
                       "Ljung_Box (R^2, Q = 15) pv",
                       "Ljung_Box (R^2, Q = 20) pv",
                       "LM Arch pv",
                       "BIC",
                       "RMSE",
                       "MAE",
                       "MAPE",
                       "AMAPE")
df_AG_2
do.call(grid.arrange, c(plot_list, ncol = 2))
```
Looks like bad forecast values.
As a result, in terms of forecasting accuracy, just use the original arma(1,1) + garch(1,1) model.